### 2012-05-14 trunk/paper-iswc-reification/rep.tex
some clarifications

\todo{introduce this subsection (explain the purpose of the conversion function defined here)}

For any RDF triple $(s,p,o) \in (\symAllURIs \cup \symAllBNodes) \times \symAllURIs \times (\symAllURIs \cup \symAllBNodes \cup \symAllLiterals)$ and blank node $b \in \symAllBNodes$ we define:
\begin{align*}
	\mathrm{reif}\bigl( s,p,o, b \bigr) := \big\lbrace
		& (b,\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}),
		(b,\mathTinyRDF{rdf\!:\!subject},s), \\
		& (b,\mathTinyRDF{rdf\!:\!predicate},p),
		(b,\mathTinyRDF{rdf\!:\!object},o)
	\big\rbrace
\end{align*}

\noindent
Let $G$ be a set of {\RDFplusTriple}s. For converting $G$ into a set of RDF triples we assume a bijective function $id : \fctTRef{G} \rightarrow B$ where $B \subset \symAllBNodes$ is a set of blank nodes such that $| B | = | \fctTRef{G} |$ and $B \cap \fctTerms{G} = \emptyset$. Hence, $id$ associates each {\TRef} in $G$ with a fresh blank node (not used in $G$). Furthermore, we introduce
	%an injective function $id^* : \fctTerms{G} \rightarrow \fctTerms{G} \cup B$
	another bijective function $id^*\! : \fctTerms{G} \rightarrow B \cup \bigl( \fctTerms{G} \!\setminus\! \fctTRef{G} \bigr)$
that is defined as follows: Let $x \in \fctTerms{G}$. If $x \in \symAllTRefs$ then $id^*\!(x) := id(x)$; if $x \notin \symAllTRefs$ then $id^*\!(x) := x$.
%
	Using $id^*$,
	%Overloading function $\mathrm{reif}$,
for any {\TRef} $r = (s,p,o) \in \fctTRef{G}$ we define:
% \vspace{-3mm} % Layout Adjustment
\begin{equation*}
	\mathrm{reif}( r ) := \mathrm{reif}\bigl( \, id^*\!(s), id^*\!(p), id^*\!(o), id^*\!(r) \, \bigr)
\end{equation*}

@@

\noindent
Finally:
\begin{equation*}
	\fctDescent{G} := \bigcup_{t \in G} \fctDescent{t}
\end{equation*}

>>>>

Let $G$ be a set of {\RDFplusTriple}s. For \Todo{converting}{introduce this subsection (explain the purpose of the conversion function defined here)} $G$ into a set of RDF triples we assume a bijective function $id : \fctTRef{G} \rightarrow B$ where $B \subset \symAllBNodes$ is a set of blank nodes such that $| B | = | \fctTRef{G} |$ and $B \cap \fctTerms{G} = \emptyset$. Hence, $id$ associates each {\TRef} in $G$ with a fresh blank node (not used in $G$). Furthermore, we introduce
	%an injective function $id^* : \fctTerms{G} \rightarrow \fctTerms{G} \cup B$
	another bijective function $id^*\! : \fctTerms{G} \rightarrow B \cup \bigl( \fctTerms{G} \!\setminus\! \fctTRef{G} \bigr)$
that is defined as follows: Let $x \in \fctTerms{G}$. If $x \in \symAllTRefs$ then $id^*\!(x) := id(x)$; if $x \notin \symAllTRefs$ then $id^*\!(x) := x$.
%
Using $id^*$, for any {\TRef} $r = (s,p,o) \in \fctTRef{G}$ we define:
\begin{align*}
	\mathrm{reif}\bigl( r \bigr) := \big\lbrace
		& (id^*\!(r),\mathTinyRDF{rdf\!:\!type},\mathTinyRDF{rdf\!:\!Statement}),
		(id^*\!(r),\mathTinyRDF{rdf\!:\!subject},id^*\!(s)), \\
		& (id^*\!(r),\mathTinyRDF{rdf\!:\!predicate},id^*\!(p)),
		(id^*\!(r),\mathTinyRDF{rdf\!:\!object},id^*\!(o))
	\big\rbrace
\end{align*}

@@

\noindent
\Todo{Finally}{add some more text here}:
\begin{equation*}
	\fctDescent{G} := \bigcup_{t \in G} \fctDescent{t}
\end{equation*}
